cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Added overall paragraph for S-curev data

>>>>

An S-curve structure simulates data that lies along a smooth, non-linear manifold, making it a classic example for testing the performance of non-linear dimension reduction methods. This package provides functions to generate standard S-curve shapes as well as variants containing holes to introduce missing or incomplete regions. These variations are useful for evaluating how well algorithms capture non-linear geometry and handle incomplete manifolds in high-dimensional data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:scurve-tb-html)', '\\@ref(tab:scurve-tb-pdf)'))` summarizes these functions.

### 2025-06-24 paper-cardinalR.tex
Added overall paragraph for S-curev data

>>>>

An S-curve structure simulates data that lies along a smooth, non-linear manifold, making it a classic example for testing the performance of non-linear dimension reduction methods. This package provides functions to generate standard S-curve shapes as well as variants containing holes to introduce missing or incomplete regions. These variations are useful for evaluating how well algorithms capture non-linear geometry and handle incomplete manifolds in high-dimensional data. Table \ref{tab:scurve-tb-pdf} summarizes these functions.
